### 2010-11-14 docs/tex/mimicry.tex
Changed the name of the chapters.
Small updates

%Chapter describing the mimetic process
\chapter{Mimicry}

@@

``According to punctuated equilibrium, there, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories. Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}. The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}

>>>>

%Chapter describing the mimetic process
\chapter{The Inspiration: Mimicry}

@@

``According to punctuated equilibrium, therefore, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories. Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}. The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}
